Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-24 BN_discretizer_paper.tex
find a typo

\noindent
where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\lambda$ representation is the number of instances within each discretization interval.

>>>>

\noindent
where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
